% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yongjin Dai}

\basicInfo{
  \email{yongjindai09@gmail.com} \textperiodcentered\
  \phone{(+86) 158-5072-7131} \textperiodcentered\
  \wechat{goldenginkgo} \textperiodcentered\
  \linkedin[yongjindai]{https://www.linkedin.com/in/yongjindai}}

\section{\faCogs\ IT Skills}
\begin{itemize}[parsep=0.5ex]
%  \item Programming Languages: C == Python > C++ > Java
  \item Back-end: Ruby, Ruby on Rails, Python, Java.
  \item Front-end: HTML, CSS, JavaScript, jQuery, JSON, Bootstrap, Sass.
  \item Database: SQL/NoSQL, PostgreSQL, Redis.
  \item Testing: TDD, BDD, Jenkins, RSpec, Capybara, Cucumber, Selenium.
  \item Source Code Management: Git, SVN.
  \item Operating Systems: Linux (Red Hat, CentOS, Ubuntu), Windows Server.
  \item Virtualization and Cloud Platforms: VMware vSphere, KVM, OpenStack.
\end{itemize}

\section{\faUsers\ Work Experience}
\datedsubsection{\textbf{Fujitsu Nanda Software Technology} Nanjing}{2011 -- 2016}
\role{Software Engineer}{}
\begin{itemize}
  \item Analyze requirements, design, implement and test new features for cloud products.
  \item Support legacy systems and solve customer issues.
\end{itemize}

\section{\faTasks\ Projects}
\datedsubsection{\textbf{Fujitsu Cloud Service K5 (K5)}}{2015 -- 2016}
\role{Ruby on Rails, Python}{}
K5 is based on OpenStack and Cloud Foundry, and provides similar service as Amazon's AWS.
\begin{itemize}
  \item Implemented RESTful APIs for Region Manager (Web Application for OpenStack Management).
  \item Installed and configured OpenStack environments with high availability. Investigated and found a solution to upgrade OpenStack without stopping instances.
  \item Solved 30+ OpenStack usage problems, including 4 source bugs about instance live migration and OpenStack Heat, and contributed to the OpenStack community by fixing three documentation bugs.
\end{itemize}

\datedsubsection{\textbf{Fujitsu ServerView Resource Orchestrator Cloud Edition (ROR CE)}}{2011 -- 2015}
\role{Ruby on Rails, Python}{}
ROR CE is a private cloud product similar to OpenStack.
\begin{itemize}
  \item Designed and implemented a new automated disaster recovery solution to protect the continuity of IT services, bringing more than five big corporate customers.
  \item Implemented a VMware vCenter Server simulator, and utilized the simulator to write automation scripts to create virtual machines for performance testing.
  \item Tuned performance issues and refactored code logic, reducing recovery time objective (RTO) by 90 percent in the case of 1000 instances.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Nanjing University (NJU)}, Nanjing, China}{2007 -- 2011}
\textit{B.Eng.} in Software Engineering
\begin{itemize}
  \item People's Scholarship
  \item National Endeavor Fellowship
\end{itemize}

%\section{\faHeartO\ Honors and Awards}
%\datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
%\datedline{Other awards}{2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
%  \item Blog: http://goldginkgo.me/
%  \item GitHub: https://github.com/goldginkgo
  \item Languages: English - Fluent, IELTS 6.5
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
